---
title: "Assignment 13 - Shiny and Maps (4 pts)"
author: "Group 7, Aditya Kannoth (ank4an)"
date: "Due Date: 11:59pm, Apr 4"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
# runtime: shiny    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
library(tidyverse)
library(shiny)
library(shinythemes)
```

# Group Homework 

- You will work with your group to complete this assignment.

- Upload your Shiny app on [ShinyApps.io](https://www.shinyapps.io).

- Submit your group's shared `.Rmd` AND your URL (https://XXXXX.shinyapps.io/XXXXX) on Collab.

- Confirm this with the following comment included in your submission text box: **"Honor Pledge: I have recreated my group submission using using the tools I have installed on my own computer"**
    
- Name the files with a group name and YOUR name for your submission.

- One of the group members will **present R codes and plots for Parts 1 and 2** in class on **Apr. 4 (Mon)**. Please e-mail the instructor if you're a presenter by 11:59pm, Apr. 3. Also, if you're a presenter, please bring your laptop so that you can share your screen on zoom for the presentation.

# Part 1

- Get the latest data from from [https://covid19.who.int/info?openIndex=2](https://covid19.who.int/info?openIndex=2).
      
   - The file should likely be named "WHO-COVID-19-global-table-data.csv"
      
   - Don't use the data for the previous group assignments. It is not the most recent data. 

- Choose three WHO regions of interest. Note that we have 6 main regions: Africa, Americas, Eastern Mediterranean, Europe, South-East Asia, and Western Pacific.

- Create a subset including 3 countries per `WHO region`. You can choose any three countries within each `WHO region` to compare the mortality rate (`mutate(rate = "Deaths - cumulative total"/"Cases - cumulative total")`). You will have 9 countries (3 countries * 3 WHO regions).

- Using `navbarPage()`, create a shiny dashboard that contains 3 tabs where each tab has a barplot of mortality rates with error bars from three countries in the selected region. For example,

```
ui <- navbarPage(title = "Mortality Rate", 
      tabPanel("Africa", ...), 
      tabPanel("Americas", "...), 
      tabPanel("Eastern Mediterranean", ...))
```      
- Create separate `tabPanel()` for each level of`WHO region` variable.

- Under each tab, create a bar plot (with error bars) from three countries in the selected region with a controller for including/excluding errors bars. The default plot has no error bars.

- Use different control types under each tab. Check available control types from [Widget gallery](https://shiny.rstudio.com/gallery/widget-gallery.html).
  
- Change a theme from the `shinythemes` package. See options from https://rstudio.github.io/shinythemes/.   

- Tips for  `renderPlot()`:

```
    output$<id> = renderPlot({
     
     p1 <-  ...your ggplot...
     print(p1)
      
     if (input$<id>) { # modify this line
     p1_e <- p1 + geom_errorbar(aes(ymin=rate-1.96*SE, ymax=rate+1.96*SE), width=.2)  # add error bars
     print(p1_e)
     }}) 
```

- Example: https://youmi.shinyapps.io/A13part1/

```{r}
# dir <- "C:/Users/Aditya Kannoth/Desktop/School/SPRING2022/DS 3003/Assignment13"
# setwd(dir)

library(readr)
covid <- read_csv("WHO-COVID-19.csv")

subset <- c('Botswana', 'Cabo Verde', 'Cameroon', 'Aruba', 'Belize', 
           'Bermuda', 'Egypt', 'Jordan', 'Kuwait', 'Austria', 'Belgium', 'Bosnia and Herzegovina', 'India', 'Myanmar', 'Nepal', 'Cambodia', 'Fiji', 'French Polynesia')

covid_subset <- covid %>% filter(Name %in% subset) %>% 
  mutate(rate = `Deaths - cumulative total`/`Cases - cumulative total`,
         SE = sqrt(rate*(1-rate)/`Cases - cumulative total`))

```
```{r}
ui <- navbarPage(title = "Mortality Rate", 
      theme = shinytheme("superhero"),
      tabPanel("Africa",
               sidebarLayout(
                 sidebarPanel(
                     selectInput("e_bars", label = "Error Bars?",
                                 choices = c("Error Bars", "No Error Bars"), selected = "No Error Bars")
                 ),
                 mainPanel(
                   plotOutput("afrplot"))
                 )
               ),
      tabPanel("Americas",
               sidebarLayout(
                 sidebarPanel(
                     checkboxInput("e_bars2", label = "Error Bars?", value = FALSE)
                 ),
                 mainPanel(
                   plotOutput("ameplot"))
                 )
               ),               
      tabPanel("Eastern Mediterranean",
               sidebarLayout(
                 sidebarPanel(
                     radioButtons("e_bars3", label = h3("Error Bars?"),
                                  choices = list("Yes" = "Yes", "No" = "No"),
                                  selected = "No")
                 ),
                 mainPanel(
                   plotOutput("easplot"))
                 )
               ))

server <- function(input, output){
    
    output$afrplot <- renderPlot({
      
    p1 <- ggplot(covid_subset[covid_subset$`WHO Region` == 'Africa',], aes(x = Name, y = rate)) +
      geom_bar(stat = "identity") +
      theme_bw() + 
      labs(main = "Covid Mortality Rate of Countries in Africa", x = "Country", y = "Mortality rate")
    print(p1)
    
    if (input$e_bars == "Error Bars") {
     p1_e <- p1 + geom_errorbar(aes(ymin=rate-1.96*SE, ymax=rate+1.96*SE), width=.2)  # add error bars
     print(p1_e)
    }
    
    })
    
    output$ameplot <- renderPlot({
    
    p2 <- ggplot(covid_subset[covid_subset$`WHO Region` == 'Americas',], aes(x = Name, y = rate)) +
      geom_bar(stat = "identity") +
      theme_bw() + 
      labs(main = "Covid Mortality Rate of Countries in the Americas", x = "Country", y = "Mortality rate")
    print(p2)
    
    if (input$e_bars2 == TRUE) {
     p2_e <- p2 + geom_errorbar(aes(ymin=rate-1.96*SE, ymax=rate+1.96*SE), width=.2)  # add error bars
     print(p2_e)
    }

    })
    
    output$easplot <- renderPlot({
      
    p3 <- ggplot(covid_subset[covid_subset$`WHO Region` == 'Eastern Mediterranean',], aes(x = Name, y = rate)) +
      geom_bar(stat = "identity") +
      theme_bw() + 
      labs(main = "Covid Mortality Rate of Countries in the Eastern Mediterranean", x = "Country", y = "Mortality rate")
    print(p3)
    
        if (input$e_bars3 == "Yes") {
     p3_e <- p3 + geom_errorbar(aes(ymin=rate-1.96*SE, ymax=rate+1.96*SE), width=.2)  # add error bars
     print(p3_e)
    }

    })
    
}

shinyApp(ui = ui, server = server, options = list(height = 500)) 

```


# Part 2

- Create a choropleth US map like the Trump Impeachment example. You need to add any state-related variable (e.g., the number of universities per state, the crime rate per state) onto the US map.

- Use a dataset that is available in data repositories (e.g., [kaggle](https://www.kaggle.com/datasets)). But don't use the built-in datasets or datasets from packages. You need to find a state-related variable online. 

- Briefly describe the dataset you're using for this assignment (e.g., means to access data, context, sample, variables, etc...)
  
   + *describe your data.*
   
- Create a choropleth map that displays data on a map by shading states with different colors.

- You can use any map-related functions we've learned in class or any other available functions for creating maps. Your map can be a static map or an interactive map.

Our dataset is sourced from [Kaggle](https://www.kaggle.com/). Specifically, it contains statistics, in arrests per 100,000 residents for assault, murder, and rape in each of the 50 US states in 1973; the percent of the population living in urban areas is also given. The data frame has 50 observations and 4 variables (in addition to state).

**Data Dictionary**
State is categorical (index variable)
Murder is numeric and Murder arrests (per 100,000)
Assault is numeric and Assault arrests (per 100,000)
UrbanPop is numeric and UrbanPop arrests (per 100,000)
Rape is numeric and Rape arrests (per 100,000)

**Source and References**
World Almanac and Book of facts 1975. (Crime rates).  
Statistical Abstracts of the United States 1975. (Urban rates).  
McNeil, D. R. (1977) Interactive Data Analysis. New York: Wiley.

```{r}
library(ggplot2)
```

```{r}
crime = read.csv('crime.csv')
cat("Dimensions: ", dim(crime))
head(crime)
```

```{r}
cols = names(crime)
cols[1] = "region"
names(crime) = cols
crime$region = tolower(crime$region)
```

```{r}
states <- map_data("state")
head(states)
```

```{r}
df <- merge(
  crime, 
  states, 
  by="region"
)
head(df)
```

```{r}
ggplot(df) +
  geom_polygon(
    aes(
      x=long,
      y=lat,
      group=group, 
      fill=Murder
    )
  ) +
  coord_map() +
  theme_bw() +
  ggtitle("Murders per 100k by State") +
  theme(
    plot.title=element_text(
      face="bold", 
      hjust=0.5
    ),
    panel.grid.major=element_blank(),
    panel.grid.minor=element_blank(),
    panel.background=element_blank(), 
    panel.border=element_blank(),
    axis.text=element_blank(),
    axis.ticks=element_blank(),
    axis.title=element_blank(),
    axis.line=element_blank()
  )
```

- Describe your choropleth map.

As indicated by the lighter shaded states in the choropleth map, it is evident that states in Southeast have the most Murders per 100k. Although this is somewhat of a generalization, states such as Georgia, Mississippi, Florida, and Louisiana have some of the highest murder rates at the time. Conversely, many of the Northern states, especially those in the Midwest region, have the lowest murder rates per 100k.
