---
title: "Assignment 11 - Shiny"
author: "Group #, NAME"
date: "Due Date: 11:59pm, Mar 27"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
runtime: shiny    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
library(knitr)
library(tidyverse)
library(plotly)
library(foreign)
```

# Group Homework 

- You will work with your group to complete this assignment.

- Upload your Shiny app on [ShinyApps.io](https://www.shinyapps.io).

- Submit your group's shared `.Rmd` AND your URL (https://XXXXX.shinyapps.io/XXXXX) on Collab.

- Confirm this with the following comment included in your submission text box: **"Honor Pledge: I have recreated my group submission using using the tools I have installed on my own computer"**
    
- Name the files with a group name and YOUR name for your submission.

- One of the group members will **present R codes and plots for Parts 1 and 2** in class on **Mar. 28 (Mon)**. Please e-mail the instructor if you're a presenter by 11:59pm, Mar. 27. Also, if you're a presenter, please bring your laptop so that you can share your screen on zoom for the presentation.

# Part 1

- First, get the latest data from from [https://covid19.who.int/info?openIndex=2](https://covid19.who.int/info?openIndex=2).
      
   - The file should likely be named "WHO-COVID-19-global-table-data.csv"
      
   - Don't use the data for Group Assignment 10. It may not be the most recent data. 

- Create a subset including 3 countries per `WHO region` (Africa, Americas, Eastern Mediterranean, Europe, South-East Asia, Western Pacific). You can choose any three countries within each `WHO region` to compare the mortality rate (`mutate(rate = "Deaths - cumulative total"/"Cases - cumulative total")`). The selected countries can be the same as those for Group Assignment 10.

- Create a shiny app to produce bar plots (with error bars), along with the control type of `selectInput()`.

     - You need to use `selectInput()` in the `ui` to select one level from the `WHO region` variable (with 6 levels: Africa, Americas, Eastern Mediterranean, Europe, South-East Asia, Western Pacific). 
     
     - Your output should be a barplot of mortality rates with error bars from three countries in the selected region. 

- Example: https://youmi.shinyapps.io/A11examplePart1/

```{r}
# add your codes 
```

# Part 2

The dataset I'm using for this assignmnet is a camera dataset I found on kaggle. It contains 13 properties for over 1000 cameras, ranging from variables such as max resolution, year, model, effective pixels, etc. I'm going to take two continuous variables and see the relationship between them using a loess scatterplot and shiny.
   
The two continous variables I'm going to look at are 1) Maximum Resolution, and 2) Release Date. I'm going to try and see if there is a relationship between these variables. I feel that there should be a positive linear relationship, as I would imagine that as time goes on and technology advances, the maximum resolution for cameras should increase.

- You need to create two input variables for loess regression. 

    - One input variable is the degree with values of 0, 1, and 2.
    - The other input variable is the span value ranging from 0.2 to 0.9.
   
- You can choose appropriate control types from [Widget gallery](https://shiny.rstudio.com/gallery/widget-gallery.html).
     
```{r}

camera = read_csv("./camera_dataset.csv")
A = camera$`Max resolution`
B = camera$`Release date`

inputPanel(
  sliderInput("span", label = "Span adjustment:",
              min = 0.2, max = 0.9, value = 0.5, step = 0.1)
)

renderPlot({
  ggplot(camera, aes(x=`Max resolution`, y=`Release date`)) +
    geom_point() +
    geom_smooth(method="loess", formula=y~x, se=FALSE, span=input$span) +
    theme_bw()
})

```

- Describe a relationship between A and B. Also, describe how a loess line changes as the degree increases and/or the span value increases.

The relationship between A and B seems to be positive linear. However, towards the end (years 2004-2006), the cameras seem to not increase in max resolution so rapidly. The loess plot graphs a downward trend towards the end, but it is hard to say that this is the case in a general sense without a broader scope of data. However given this data, it seems to have positive linear growth until it reaches a plateau where it slows down. This could be because more budget and travel sized cameras were being made in those years so max resolution was not prioritized, among other reasons. As the degree and span value increases, the line tends to become more smooth. 