---
title: "Assignment 11 - Shiny"
author: "Group #, NAME"
date: "Due Date: 11:59pm, Mar 27"
output:
  html_document:
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
# runtime: shiny    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
library(knitr)
library(tidyverse)
library(plotly)
library(foreign)
```

# Group Homework 

- You will work with your group to complete this assignment.

- Upload your Shiny app on [ShinyApps.io](https://www.shinyapps.io).

- Submit your group's shared `.Rmd` AND your URL (https://XXXXX.shinyapps.io/XXXXX) on Collab.

- Confirm this with the following comment included in your submission text box: **"Honor Pledge: I have recreated my group submission using using the tools I have installed on my own computer"**
    
- Name the files with a group name and YOUR name for your submission.

- One of the group members will **present R codes and plots for Parts 1 and 2** in class on **Mar. 28 (Mon)**. Please e-mail the instructor if you're a presenter by 11:59pm, Mar. 27. Also, if you're a presenter, please bring your laptop so that you can share your screen on zoom for the presentation.

# Part 1

- First, get the latest data from from [https://covid19.who.int/info?openIndex=2](https://covid19.who.int/info?openIndex=2).
      
   - The file should likely be named "WHO-COVID-19-global-table-data.csv"
      
   - Don't use the data for Group Assignment 10. It may not be the most recent data. 

- Create a subset including 3 countries per `WHO region` (Africa, Americas, Eastern Mediterranean, Europe, South-East Asia, Western Pacific). You can choose any three countries within each `WHO region` to compare the mortality rate (`mutate(rate = "Deaths - cumulative total"/"Cases - cumulative total")`). The selected countries can be the same as those for Group Assignment 10.

- Create a shiny app to produce bar plots (with error bars), along with the control type of `selectInput()`.

     - You need to use `selectInput()` in the `ui` to select one level from the `WHO region` variable (with 6 levels: Africa, Americas, Eastern Mediterranean, Europe, South-East Asia, Western Pacific). 
     
     - Your output should be a barplot of mortality rates with error bars from three countries in the selected region. 

- Example: https://youmi.shinyapps.io/A11examplePart1/

```{r}
# add your codes 
```

# Part 2

- Use a dataset that is available in data repositories (e.g., [kaggle](https://www.kaggle.com/datasets)). But don't use the datasets you used for your previous assignments.

- Briefly describe the dataset you're using for this assignment (e.g., means to access data, context, sample, variables, etc...)
  
   + *describe your data.*
   
- Select *two* continuous variables (denoted as "A" and "B") 

- Create an interactive scatterplot between "A" and "B" with a loess line using Shiny app. Please refer to lecture notes `DS3003_localreg_loess_note.pdf`, `DS3003_localreg_loess_code.rmd`, and `DS3003_localreg_loess_code.html` 

- You need to create two input variables for loess regression. 

    - One input variable is the degree with values of 0, 1, and 2.
    - The other input variable is the span value ranging from 0.2 to 0.9.
   
- You can choose appropriate control types from [Widget gallery](https://shiny.rstudio.com/gallery/widget-gallery.html).
     
```{r}
# add your codes 
```

- Describe a relationship between A and B. Also, describe how a loess line changes as the degree increases and/or the span value increases.

